Leadership across cultures and contexts: an exploratory analysis

### 2020-05-09 leadership_across_cultures_contexts.Rmd

```{r matingbenefit}
matingbenefit <- signif(100*leader_benefits_cult$Estimate[leader_benefits_cult$Variable=='Mating benefit'], 3)
```

Most potentially universal dimensions discovered here appear in a model developed by @hagen_leadership_2019, in which knowledgeable and intelligent individuals provide computational (cognitive) services to group members in exchange for a variety of fitness benefits, and these services often involve conflict resolution and other social functions [see also @garfield_evolutionary_2019]. But the computational services model emphasizes mating benefits, which appear in `r matingbenefit`% of cultures, below our arbitrary 60% threshold for "universality". See Figure \@ref(fig:varsupportcb).

>>>>

```{r matingbenefit}
matingbenefit <- signif(100*leader_benefits_cult$Estimate[leader_benefits_cult$Variable=='Mating benefit'], 3)

reprosuccess <- signif(100*features_support_cult$Estimate[features_support_cult$Variable == 'Social_material_success'], 3)
```

Most potentially universal dimensions discovered here appear in a model developed by @hagen_leadership_2019, in which knowledgeable and intelligent individuals provide computational (cognitive) services to group members in exchange for a variety of fitness benefits, and these services often involve conflict resolution and other social functions [see also @garfield_evolutionary_2019]. The computational services model emphasizes mating benefits, however, which appear in `r matingbenefit`% of cultures, below our arbitrary 60% threshold for "universality" (see Figure \@ref(fig:varsupportcb)). But there was evidence for the "Social material success" feature, which included Polygyny, High quality spouse, and Many children, in more cultures (`r reprosuccess`%) than any other feature (see Figure \@ref(fig:featuressupportplot)). Interestingly, the computational model highlights women's family leadership role, and the estimated marginal mean for Social material success was higher for females leaders than male leaders (see Figure \@ref(fig:heatmap_feature_sex)), with the caveat that there were few text records on female leaders in our sample.
